---
title: "Vignette Title"
author: "Vignette Author"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{MY PALETTE palette demo}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

## Set Up

```{r}
library(Rtistic)
library(ggplot2)
```


```{r}
# make fake data for plots ----
points <- data.frame(x = 1:10, y = 1:10)
distrb <- data.frame(x = rep(1:6, 10), y = rnorm(60, 0, 1))

# make plots for themes ----
g_points <- ggplot(points, aes(x, y, col = factor(x))) + geom_point(size = 5)
g_distrb <- ggplot(distrb, aes(y, fill = factor(x))) + geom_density() + facet_wrap(. ~ x, ncol = 3)
g_points_cont <- ggplot(points, aes(x, y, col = x)) + geom_point(size = 5)
```

## Motivation for this Theme

ADD SOMETHING HERE!

## Key Colors

The colors in the discrete palette are:

```{r}
scales::show_col(test_pal)
```

The colors used to define the conintuous palette spectrum are:

```{r}
scales::show_col(test_pal_cont)
```

The colors used in the diverging palette are:

```{r}
scales::show_col(test_pal_div)
```


## Discrete Palettes

Consider the following plots:

```{r}
g_points
g_distrb
```

Fixed-length discrete palettes use the palette's selected colors until they run out, then it uses grey for all additional levels of the aesthetic. 

```{r}
g_points + scale_color_discrete_rtistic(palette = "test")
g_distrb +  scale_fill_discrete_rtistic(palette = "test")
```

Interpolated palettes extend the discrete palette by interpolating additional values.

```{r}
g_points + scale_color_discrete_rtistic(palette = "test", extend = TRUE)
g_distrb + scale_fill_discrete_rtistic(palette = "test", extend = TRUE)
```

Opinionated palettes color specific values for "good", "bad", and "neutral" in your dataset. 

```{r}
points$assessment <- "neutral"
points$assessment[points$x > 5] <- "good"
points$assessment[points$x < 3] <- "bad"

ggplot(points, aes(x, y, col = assessment)) + geom_point() + scale_color_opinionated_rtistic(palette = "test")
```



## Continuous Palettes

Consider the following plots:

```{r}
g_points_cont
```

Diverging palettes grow more extreme at the endpoints. You can specify the `midpoint` of where the center should be. 

```{r}
g_points_cont + scale_color_diverging_rtistic(palette = "test", midpoint = 5)
```

Normal continuous scales gradually move between two ends of a spectrum.

```{r}
g_points_cont + scale_color_continuous_rtistic(palette = "test")
```

