---
title: "Vignette Title"
author: "Vignette Author"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

## Set Up

```{r}
library(Rtistic)
library(ggplot2)
```


```{r}
# make fake data for plots ----
points <- data.frame(x = 1:10, y = 1:10)
distrb <- data.frame(x = rep(1:6, 10), y = rnorm(60, 0, 1))

# make plots for themes ----
g_points <- ggplot(points, aes(x, y, col = factor(x))) + geom_point(size = 5)
g_distrb <- ggplot(distrb, aes(y, fill = factor(x))) + geom_density() + facet_wrap(. ~ x, ncol = 3)
g_points_cont <- ggplot(points, aes(x, y, col = x)) + geom_point(size = 5)
```

## Discrete Palettes

Consider the following plots:

```{r}
g_points
g_distrb
```

Fixed-length discrete palettes use the palette's selected colors until they run out, then it uses grey for all additional levels of the aesthetic. 

```{r}
g_points + scale_color_discrete_test()
g_distrb + scale_fill_discrete_test()
```

Interpolated palettes extent the discrete palette by interpolating additional values.

```{r}
g_points + scale_color_discrint_test(points$x)
g_distrb + scale_fill_discrint_test(distrb$x)
```


## Continuous Palettes

Consider the following plots:

```{r}
g_points_cont
```

Diverging palettes grow more extreme at the endpoints. You can specify the `midpoint` of where the center should be. 

```{r}
g_points_cont + scale_color_contdiv_test(midpoint = 5)
```

Normal continuous scales gradually move between two ends of a spectrum.

```{r}
g_points_cont + scale_color_cont_test()
```

